Depression_Vis

### 2023-04-11 Depression_Vis.Rmd
ymd

Mothership$Intake_1<-mdy(Mothership$Intake_1,locale = "en_US.UTF-8")
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))

Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014",
                                   "2021"="2020",
                                   "2022"="2020"))

>>>>

Mothership$Intake_1<-ymd(Mothership$Intake_1,locale = "en_US.UTF-8")
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014",
                                   "2021"="2020",
                                   "2022"="2020"))
